\begin{description}
	\item[Luca Dusi] He contributed to the initial project setup by adding the Maven configuration, creating the first project structure, and preparing the first login and register pages with the related servlets. He also implemented important application features such as \texttt{CourseSummaryServlet}, \texttt{DownloadNoteServlet}, \texttt{FavoritesPageServlet}, updates to the register flow and \texttt{UserDAO}, the profile page, and significant changes to the upload page and JavaScript. For the report, he added the sequence diagram and the wrote  the objectives section.
	\item[Laszlo Kosa] He contributed to the user and note management part of the application by implementing the \texttt{User} model, \texttt{UserDAO}, and \texttt{NoteDAO}, and by adapting the login and registration logic to use them. He also implemented object storage support through \texttt{StorageService}, updated the database connection and dependencies, and developed the note upload functionality with its servlet and interface. In addition, he implemented \texttt{FavoriteServlet}, refined the registration page, and contributed to the documentation with the main functionalities and REST error codes sections.
	\item[Milos Trifunovic] He contributed to the core domain and business logic by implementing the \texttt{Note}, \texttt{Course}, \texttt{Rating}, and \texttt{Favorite} models, the search notes functionality, the rating servlet, the note update servlet, and further work on \texttt{RatingDAO}. He also worked on the frontend by improving the rating and favorite interactions, adding the favorites page, and reorganizing the controller structure. He prepared the database schema, initial SQL data, and the environment configuration template, and contributed heavily to the report with the data logic layer, presentation logic layer, class diagram and screenshots.
	\item[Edoardo Zanella] He contributed to repository maintenance and application features, and cleaning project files. He implemented \texttt{CourseDAO}, \texttt{RatingDAO}, \texttt{FavoriteDAO}, \texttt{LogoutServlet}, \texttt{RemoveFavoriteServlet}, \texttt{ProfileServlet}, and \texttt{DeleteNoteServlet}, and he also created the home page while extending the course data access layer. For the report, he added and refined the REST API summary and detailed REST API documentation.

\end{description}
