\section{Main Functionalities}

This section describes the main functionalities offered by the application.
The system is designed to manage user accounts, handle lecture notes, and
provide interaction mechanisms between users.

\subsection{User Management}

The application allows users to create and manage their personal accounts.
In particular, users can register, log in, log out, and update their profile
information. These features are implemented through the following components:

\begin{itemize}
    \item \texttt{RegisterServlet}
    \item \texttt{LoginServlet}
    \item \texttt{LogoutServlet}
    \item \texttt{ProfileServlet}
\end{itemize}

\subsection{Note Management}

Authenticated users can upload and manage lecture notes in PDF format.
Each note is associated with a specific course and can be modified or removed
by its owner. The system also allows users to download notes shared by others.

\begin{itemize}
    \item \texttt{UploadNoteServlet}
    \item \texttt{UpdateNoteServlet}
    \item \texttt{DeleteNoteServlet}
    \item \texttt{DownloadNoteServlet}
\end{itemize}

\subsection{Search and Organization}

To facilitate access to content, the application provides a search functionality
that allows users to find notes based on different criteria such as title,
course, or author.

\begin{itemize}
    \item \texttt{SearchNoteServlet}
\end{itemize}
Additionally, notes are organized by course, and a summary view is available
to display all notes related to a specific course.

\begin{itemize}
    \item \texttt{CourseSummaryServlet}
\end{itemize}

\subsection{User Interaction Features}

The platform includes features that enhance user interaction and content evaluation.

\begin{itemize}
    \item \textbf{Favourites:} users can save notes in a personal favourites list
    and access them through a dedicated page (\texttt{favorites.jsp}).

    \item \textbf{Ratings:} users can rate notes uploaded by other students,
    contributing to an overall quality score.
\end{itemize}