\section{Presentation Logic Layer}

After defining the data model of the application, this chapter describes the
presentation layer, which is responsible for user interaction through the web interface.

The presentation layer is implemented using JSP pages located in
\texttt{src/main/webapp/jsp/}. The application entry point is \texttt{login.jsp},
as specified in the \texttt{web.xml} configuration file.

\subsection{Login Page -- \texttt{login.jsp}}
Presents a form for user authentication (username and password).
On success the user is redirected to the home page.

\subsection{Register Page -- \texttt{register.jsp}}
Allows new users to create an account by providing username, email, and password.

\subsection{Home Page -- \texttt{home.jsp}}
The main dashboard after login. Displays the list of available notes with
search and filter controls. Users can browse by course, download notes,
or add them to favourites directly from this page.

\subsection{Upload Page -- \texttt{upload.jsp}}
Form for uploading a new note: the user selects the course, inserts a title
and description, and attaches a PDF file.

\subsection{Profile Page -- \texttt{profile.jsp}}
Shows the user's personal information and the notes they have uploaded.
Allows updating profile data and deleting own notes.

\subsection{Favourites Page -- \texttt{favorites.jsp}}
Lists all notes that the logged-in user has marked as favourite.

\vspace{1cm}

\begin{center}
    \textit{Each page is designed to provide a simple and intuitive user experience,
        ensuring easy navigation and efficient interaction with the system.}
\end{center}